The Evolution of Gene Expression in the Term Placenta of Viviparous Mammals

### 2016-04-28 poster/placenta_viviparous_poster.Rnw
KISS1 is not CGA
update the hypotheses to match the conclusions better

  \block{Introduction}{
\begin{itemize}
\item Function and Evolution of Placenta
    \begin{itemize}
    \item Major function is the transfer of nutrients, oxygen, and
      waste between mother and offspring
    \item Highly variable structure and form in mammals, even though
      major function is conserved
    \item Likely arose before the origin of therian mammals
    \item Form relatively well characterized, but diversity of
      molecular environment understudied
    \item Role in the evolutionary interplay between maternal and fetal
      strategies
    \end{itemize}

  \item Impacts on Human Health
    \begin{itemize}
    \item Humans possess a deeply invasive trophoblast layer that can
      penetrate the myometrium of the uterus
      \cite{Carter.ea2011:Evolutionofinvasiveplacentation}.
    \item Defects in placental growth can lead to pre-eclampsia, which can
      cause hypertension, proteinuria, and mortality of mother and/or
      infant \cite{Chaiworapongsa.ea2014:Pre-eclampsiapart1current}.
    \item Pre-eclampsia has been seen in \textit{Pan troglodytes}
      \cite{Stout.ea1969:Glomerularcapillaryendothelialswelling}, and
      \textit{Gorilla gorilla}
      \cite{Thornton.ea1992:Convulsionsinpregnancyin}
    \item Far higher incidence in \textit{Homo sapiens}, with as many as 
      4\% of pregnancies United States affected
      \cite{Chaiworapongsa.ea2014:Pre-eclampsiapart1current}.
    \end{itemize}

  \item Hypotheses
    \begin{itemize}
    \item Gene expression patterns correlate with placenta morphology
    \item Altered expression of genes correlates with invasiveness, and
      therefore pre-eclampsia
    \item Maternal/Fetal evolutionary strategies will be reflected in gene
      expression patterns
    \end{itemize}
  \end{itemize}

@@

\block{\textit{CGA} Expression}{

>>>>

  \block{Introduction}{
\begin{itemize}
\item Function and Evolution of Placenta
    \begin{itemize}
    \item Major function is the transfer of nutrients, oxygen, and
      waste between mother and offspring.
    \item Highly variable structure and form in mammals, even though
      major function is conserved.
    \item Likely arose before the origin of therian mammals.
    \item Form relatively well characterized, but diversity of
      molecular environment understudied.
    \item Role in the evolutionary interplay between maternal and fetal
      strategies.
    \end{itemize}

  \item Impacts on Human Health
    \begin{itemize}
    \item Humans possess a deeply invasive trophoblast layer that can
      penetrate the myometrium of the uterus
      \cite{Carter.ea2011:Evolutionofinvasiveplacentation}.
    \item Defects in placental growth can lead to pre-eclampsia, which can
      cause hypertension, proteinuria, and mortality of mother and/or
      infant \cite{Chaiworapongsa.ea2014:Pre-eclampsiapart1current}.
    \item Pre-eclampsia has been seen in \textit{Pan troglodytes}
      \cite{Stout.ea1969:Glomerularcapillaryendothelialswelling}, and
      \textit{Gorilla gorilla}
      \cite{Thornton.ea1992:Convulsionsinpregnancyin}.
    \item Far higher incidence in \textit{Homo sapiens}, with as many as 
      4\% of pregnancies United States affected
      \cite{Chaiworapongsa.ea2014:Pre-eclampsiapart1current}.
    \end{itemize}

  \item Hypotheses
    \begin{itemize}
    \item Mechanisms of maintaining maternal-fetal tolerance will be
      conserved.
    \item Altered expression of genes correlates with invasiveness,
      and therefore pre-eclampsia
    \item Maternal/Fetal evolutionary strategies will be reflected in
      gene expression patterns
    \end{itemize}
  \end{itemize}

@@

\block{\textit{KISS1} Expression}{
